Coupling PDEs on 3D-1D domains with Lagrange multipliers

### 2020-02-28 unfitted_prob2.tex
Updates from Overleaf

\def\patch{\omega _j}
\subsection{$\mathcal{T}^{\Omega}_h$ non conforming to $\Gamma$} \label{sec:unfit2}
We analyze now the case in which the elements of the 3D mesh $\mathcal{T}^{\Omega}_h$ cut the interface $\Gamma$. The formulation of Problem 2 is more suitable for this purpose. 
%{\color{red} Add more details, we can refer also to cutFEM (Burman, Massing etc.) explaining the limitation of that approach (network case for example).}\\
Therefore we focus on the analysis of Problem 2.

\subsubsection{Problem 2} We consider for the solutions $u_h$ and ${\ud}_h$ the spaces $X_{h,0}^1(\Omega)$ and $X_{h,0}^1(\Lambda)$. Notice that in this case we assume that the mesh sizes of the 3D mesh $\mathcal{T}^{\Omega}_h$ and the 1D mesh $\mathcal{T}^{\Lambda}_{h'}$ are different, in particular we assume the 1D mesh is finer. Concerning the multiplier space, let $\mathcal{G}_h = \{K \in \mathcal{T}^{\Omega}_h: \, K\cap \Lambda \neq \emptyset\}$, namely $\mathcal{G}_h$ is the set of the 3D elements which intersect $\Lambda$. Then we define $Q_h=\{{\ld}_h : {\ld}_h \in P^0(K) \, \forall K \in \mathcal{G}_h\}$. We notice that we are extending the multiplier to the 3D elements so that we do not need to consider the 1D mesh given by the intersection of the elements of $\mathcal{T}^{\Omega}_h$ with $\mathcal{T}^{\Lambda}_{h'}$. With this choice of multipliers the problem is not inf-sup stable, therefore the idea is to add a stabilization term $s({\ld}_h, {\md}_h)$ to \eqref{eq:prob2_discrete} following the approach introduced in \cite{burman2014}. The stabilization operator is based on a new multiplier space $L_H$ for which the discrete inf-sup condition is fulfilled and a projection operator $\pi_L: Q_h \rightarrow L_H$ such that for any $[v, \vd] \in X $
\begin{equation}\label{condition_pi_L}
b([v, \vd], {\ld}_h - \pi_L {\ld}_h) \lesssim \vertiii{[v,\vd]}\|{\ld}_h - \pi_L {\ld}_h\|_{L_H},
where for $X$ and $\vertiii{[\cdot, \cdot]}$ we use the definitions of section $3.2$ and $\|\cdot \|_{L_H}$ denotes a suitable discrete norm on $L_H$. Then, the following relaxed form of the inf-sup condition is satisfied,
\begin{lemma}\cite[Lemma2.1]{burman2014}
Under the previous assumption, $\forall {\ld}_h \in Q_h$,
\|{\ld}_h\|_{H^{-\frac 12}(\Lambda)} \lesssim \sup_{\substack{v_h \in X_{h,0}^1(\Omega)\\ {\vd}_h \in X_{h,0}^1(\Lambda)}} \frac{b([v_h, {\vd}_h], {\ld}_h)}{\vertiii{[v_h, {\vd}_h]}} + \|{\ld}_h - \pi_L {\ld}_h\|_{L_H}.
 Based on this projection operator, we build the stabilization term $s({\ld}_h, {\md}_h)$ satisfying
 \|{\ld}_h- \pi_L {\ld}_h\|_{L_H} \lesssim s({\ld}_h, {\ld}_h)
\end{equation*}  and prove that $\forall [u_h, {\ud}_h]$, there exists a function $\xi_h\in Q_h$ depending on $[u_h, {\ud}_h]$, namely $\xi_h=\xi_h([u_h, {\ud}_h])$, s.t.
\begin{equation}\label{stab_coercivity}
a([u_h, {\ud}_h],[u_h, {\ud}_h] ) + b([u_h, {\ud}_h], \xi_h) \geq \alpha_\xi \vertiii{[u_h, {\ud}_h]}_{X_{h,0}^1(\Omega)\times X_{h,0}^1(\Lambda) },
\begin{equation}\label{stab_stability}
(s(\xi_{h}, \xi_{h}))^{\frac 12} \leq c_s \vertiii{[u_h, {\ud}_h]}_{X_{h,0}^1(\Omega)\times X_{h,0}^1(\Lambda) },
being $\vertiii{[\cdot \, ,\, \cdot] }_{X_{h,0}^1(\Omega)\times X_{h,0}^1(\Lambda) }$ a suitable discrete norm. Then, the final objective of this section is to prove that the stabilized version of the 3D-1D-1D problem, precisely,
\begin{multline}\label{eq:prob2_stabilized}
a([u_h, {\ud}_h], [v_h, {\vd}_h]) +
b([v_h, {\vd}_h], {\ld}_h) +\\
b([u_h, {\ud}_h], {\md}_h) 
- s({\ld}_h, {\md}_h) = c(v_h) + d({\md}_h)\\
  \qquad \forall [v_h, {\vd}_h] \in {X_{h,0}^1(\Omega)\times X_{h,0}^1(\Lambda), \, \forall \md}_h \in Q_h
\end{multline}
is well posed.
%\begin{lemma}\cite[Lemma2.3]{burman2014}
%Under the previous assumptions, system \eqref{eq:prob2_stabilized} admits a unique solution $\{[u_h, {\ud}_h], {\ld}_h \}$.
%\end{lemma}
In what follows we discuss the definition of the space $L_H$, the projector $\pi_L$ and the stabilization operator such that lemmas 2.1 and 2.3 of \cite{burman2014} can be applied to problem \eqref{eq:prob2_stabilized}. 
We recall that in the case of Problem 2, 
b([u_h, {\ud}_h], {\ld}_h) = \left(\mtrace u_h - {\ud}_h, {\ld}_h\right)_{\Lambda,|\DD|}.
The construction of the inf-sup stable space $L_H$ is based on macro elements of diameter $H$, where $H$ is sufficiently large. In particular, we assume that there exists positive constants $c_h$ and $c_H$ such that $c_h h\leq H \leq c_H^{-1}h$. The space is constructed assembling the 3D elements of $\mathcal{G}_h$ into macro patches $ \patch $ such that $H \leq |\patch\cap \Lambda|\leq cH$, with $c\geq 1$. Let $M_j$ be the number of elements of the patch $\omega_j$, namely, $\patch=\cup _{i=0}^{M_j} K_i$, where $K_i \in \mathcal{G}_h$, $M_j$ is uniformly bounded in $j$ by some $M\in \mathbb{N}$ and $H=\min_{j}|\patch\cap \Lambda|$. We assume that the interiors of the patches $\patch$ are  disjoint. We define 
L_H=\left\{{\lld }_H: \, {\lld }_H\in P^0(\patch)\, \forall j \right\}.

@@

Moreover, we associate to each patch $\patch$ a shape-regular extended patch, still denoted by $\omega_j$ for notational simplicity, which is built adding to $\patch$ a sufficient number of elements of $\mathcal{T}_h^{\Omega}$ and we assume that the interiors of the new extended patches $\omega _j$ are still disjoint (see Figure \ref{fig:patch}). Here we are using the classical definition of shape-regularity, see for example \cite{MR2050138}, namely there exist a constant $C>0$ such that for any $\omega_j$, $\frac{\tilde{\rho}_j}{\bar{\rho}_j}\leq C$, being $\tilde{\rho}_j$ the diameter of $\omega_j$ and $\bar{\rho}_j$ the diameter of the largest ball that can be inscribed in $\omega_j$. The extended patches $\omega _j$ are built such that they fulfill the conditions meas$(\patch)=\mathcal{O}(H^3)$ and diam$(\Gamma_{\patch\cap \Lambda}\cap \omega_j)=\mathcal{O}(H)$, where $\Gamma_{\patch\cap \Lambda}$ is the portion of $\Gamma$ with centerline $\patch\cap \Lambda$. See Figure \ref{fig:gamma_generated} for a representation in the simple case in which $\omega _j$ is composed just by one tetrahedron. The latter assumption is required to ensure that the intersection of $\Gamma_{\patch\cap \Lambda}$ and $\omega_j$ is not too small and it will be needed later on to prove the inf-sup stability of the space $L_H$ in Lemma \ref{lemma:Lh_infsup}. We introduce the following discrete norms
\begin{equation*}
\|\, \lambda \,\|_{\pm \frac 12, h, \Lambda} = \|h^{\mp\frac 12} \lambda\|_{L^2(\Lambda)},
\end{equation*}
recalling that $h$ is the mesh size of $\mathcal{T}^\Omega_{h}$. We equipe the space $X_h(\Omega)\times X_{h'}(\Lambda)$ with the discrete norm
\begin{equation*}
\vertiii{[u_h, {\ud}_h]}^2_{X_h(\Omega)\times X_{h'}(\Lambda) }
= \|u_h\|^2_{H^1(\Omega)}+\|{\ud}_h\|^2_{H^1(\Lambda),|\D|} + \|\mtrace u_h - {\ud}_h\|^2_{\frac 12, h, \Lambda, |\DD|},
\end{equation*}
and the space $L_H$ with the norm 
\begin{equation*}
\|{\lld}_H \|_{L_H} = \|{\lld}_H \|_{-\frac 12, h, \Lambda}.
\end{equation*}
As shown in \cite[Section III]{burman2014}, we can always choose $\pi_L$ as the $L_2$ orthogonal projection operator from $\Lambda_h$ to $L_H$ in order to satisfy \eqref{condition_pi_L} and then in practice replace it with any interpolation $\tilde{\pi}_L$ of $\Lambda_h$ in $L_H$. In particular, we define $\forall \lambda_h \in \Lambda_h$,
\begin{equation*}
\tilde{\pi}_L {\ld}_{ _{|\patch}} = M^{-1} \sum_{\substack{i: \ K_i \in \mathcal{G}_h, \  K_i \cap \omega_j \neq \emptyset}} {\ld}_{|K_i} \qquad \text{for all $\omega_j$,} 
\end{equation*}
being $M$ the cardinality of the set $\{i: \ K_i \in \mathcal{G}_h, \  K_i \cap \omega_j \neq \emptyset\}$. These choices lead to the following stabilization 
\begin{equation}\label{eq:stab}
s({\ld}_h, {\md}_h)= \sum _{K\in \mathcal{G}_{h}} \int_{\partial K\setminus \partial \mathcal{G}_{h}} h \llbracket {\ld}_h \rrbracket \llbracket {\md}_h \rrbracket,
\end{equation}
being $\llbracket {\ld}_h \rrbracket$ the jump of ${\ld}_h$ across the internal faces of $\mathcal{G}_h$.

\begin{figure}\label{fig:gamma_generated}
\centering
\subfigure[$\Gamma_{\omega_j \cap \Lambda}$]
{
\input{./graphics/gamma_generated}
}
\qquad \qquad
\subfigure[ $\Gamma_{\omega_j \cap \Lambda} \cap \omega_j$]{
\input{./graphics/intersection}
}
\caption{$\Gamma_{\omega_j \cap \Lambda}$, the portion of $\Gamma$ generated by $\omega_j \cap \Lambda$ in (a) and the intersection between $\Gamma_{\omega_j \cap \Lambda}$ and $\omega_j$ in (b). Here for simplicity $\omega_j$ is represented as a single tetrahedron but actually it is a collection of tetrahedra as shown in Figure \ref{fig:patch}.}
\end{figure}
Thanks to the shape regularity of these extended patches, we have that the following discrete trace and Poincarè-type inequalites hold. More precisely, for any function $v\in H^1(\omega_j)$, 
\begin{equation}\label{discr_trace_ineq}
\|\trace v\|_{L^2(\Gamma\cap \omega_j)} \lesssim H^{-\frac 12} \|v\|_{L^2(\omega_j)}
\begin{equation}\label{disc_poincare_ineq}
\|v- \mathcal{E}_{\patch} \pi_L\mtrace v\|_{L^2(\omega_j)} \leq c_P H \|\nabla v\|_{L^2(\omega_j)}.
%where $\pi_L$ is a projection operator onto piecewise constant functions on $\patch\cap \Lambda$. In particular, for any $w \in L^2(\Lambda)$, we define
For any $w \in L^2(\Lambda)$ we have that $ \mathcal{E}_{\patch}\pi_Lw \in L_H$, where with a little abuse of notation we denote as $\pi_L$ the operator
\begin{equation}\label{eq:projector}
\pi_Lw_{|\patch \cap \Lambda} =\frac{1}{|\Gamma_{\patch\cap \Lambda}|}\int_{\patch\cap \Lambda}|\DD| w\quad \forall j,
whereas the operator $\mathcal{E}_{\patch}$ simply extends the constant $\pi_L\mtrace v_{|\patch \cap \Lambda}$ to $\omega _j$.
Moreover $\forall u_h \in X^1_{h,0}(\Omega)$ we have the following average inequality 
%\begin{equation*}
%\sum _j \|\mtrace u_h\|^2_{L^2(\patch \cap \Lambda),|\DD| } \leq \sum _j \|\trace  u_h\|^2_{L^2(\omega_j\cap \Gamma)}.
%\end{equation*}
which is a consequence of the definition of $\mtrace$ and Jensen inequality,
\begin{multline}\label{eq:avrg_ineq}
\sum _j \|\mtrace u_h\|^2_{L^2(\patch \cap \Lambda),|\DD| }
= \sum _j\int_{\patch \cap \Lambda} |\DD| \mtrace u_h^2 
= \int_{\Lambda} |\DD| \left( \frac{1}{|\DD|} \int_{\DD} \trace u_h \right)^2
\leq \int_{\Lambda} \int_{\DD} (\trace u_h)^2
= \int_{\Gamma} (\trace u_h)^2
= \sum _j \int_{\patch \cap \Gamma} (\trace u_h)^2
= \sum _j \|\trace u_h\|^2_{L^2(\patch \cap \Gamma)}.
\end{multline}
To prove that \eqref{eq:prob2_stabilized} is well posed, we proceed through three main steps. The first step consists of showing that the space $L_H$ is inf-sup stable. This result is addressed in the following lemma. 
\begin{lemma}\label{lemma:Lh_infsup}
The space $L_H$ is inf-sup stable, namely $\forall {\lld}_H \in L_H$, $\exists \beta >0$ s.t.
\sup_{\substack{v_h \in X_{h,0}^1(\Omega),\\ {\vd}_h \in X_{h',0}^1(\Lambda)}} \frac{\left(\mtrace v_h - {\vd}_h, {\lld} _H\right)_{\Lambda, |\DD|}}{\vertiii{[v_h, {\vd}_h]}} \geq \beta \|{\lld}_H\|_{H^{-\frac 12}(\Lambda)}.
% We have to prove that $\exists \beta >0$ such that $\forall l_h \in L_h$,
%\begin{equation*}
%\sup_{\substack{v_h \in X_{h,0}^1(\Omega),\\ {\vd}_h \in X_{h',1}^0(\Lambda)}} \frac{\left(\avrc{T v_h} - {\vd}_h, l _h\right)_{\Lambda, |\DD|}}{\vertiii{[v_h, {\vd}_h]}} \geq \beta \|l_h\|_{H^{-\frac 12}(\Lambda)}.
%\end{equation*}
As in the continuous case, we can choose ${\vd}_h=0$ and we prove that
\sup_{v_h \in X_{h,0}^1(\Omega)} \frac{\left(\mtrace v_h ,{\lld}_H\right)_{\Lambda, |\DD|}}{\|v_h\|_{H^1(\Omega)}} \geq \beta \|{\lld}_H\|_{H^{-\frac 12}(\Lambda)}.
Proving the last inequality it is equivalent to find the Fortin operator $\pi_F: H^1_0(\Omega) \rightarrow X_{h,0}^1(\Omega)$, such that 
\left(\mtrace v - \mtrace \pi _F v  , {\lld}_H\right)_{\Lambda, |\DD|}=0, \quad \forall v\in H^1_0(\Omega), \, {\lld}_H \in L_H
and
\begin{equation}\label{eq:cont_Fortin}
\|\pi_F v\|_{H^1(\Omega)}\lesssim \|v\|_{H^1(\Omega)}.

@@

\left(\mtrace v - \mtrace \pi _F v  , {\lld}_H\right)_{\Lambda, |\DD|} = \sum _j \int_{\patch\cap \Lambda} |\DD |\left[ \mtrace v-\mtrace I_h v-\sum _i \alpha_i \mtrace \varphi _i \right]{\lld}_H \\
(\text{supp} (\mtrace \varphi _i )\subset \omega _i\cap \Lambda \, \forall i)  =\sum _j \int_{\patch\cap \Lambda}|\DD| \left[ \mtrace v-\mtrace I_h v-\alpha_j \mtrace \varphi _j \right]{\lld}_H\\
=\sum _j \int_{\patch\cap \Lambda} |\DD| (\mtrace v-\mtrace  I_h v) {\lld}_H - \frac{\int_{\patch\cap \Lambda} |\DD| (\mtrace v-\mtrace I_h v)}{\int_{\patch\cap \Lambda}|\DD|\mtrace \varphi _j} \int_{\patch\cap \Lambda} |\DD|\mtrace \varphi _j{\lld}_H\\ 
(\text{using ${\lld}_H$ constant on $\patch\cap \Lambda$})=0.

@@

{\xi_h}_{|\patch\cap \Lambda}=\delta \frac 1H \pi_L(\mtrace u_h-{\ud}_h)_{|\patch \cap \Lambda}.

@@

The inequalities \eqref{stab_coercivity} and \eqref{stab_stability} are satisfied (under the previous assumptions).

@@

Concerning the coercivity property \eqref{stab_coercivity}, we have to show that $\forall [u_h, {\ud}_h]$, there esists $\xi_h \in Q_h$ s.t.

@@

(u_h,u_h)_{H^1(\Omega)}+ ({\ud}_h, {\ud}_h)_{H^1(\Lambda), |\D|} +   (\mtrace u_h - {\ud}_h, \xi_h)_{\Lambda,|\DD|} \geq \alpha_{\xi}\vertiii{[u_h, {\ud}_h]}^2_{X_h(\Omega)\times X_{h'}(\Lambda) }.

@@

and choosing $\delta=\frac{1}{4c_P^2}$ we obtain the desired inequality.\\

>>>>

\def\patch{\omega _j}
\subsection{$\mathcal{T}^{\Omega}_h$ non conforming to $\Gamma$ and $\Lambda$} \label{sec:unfit2}
We analyze now the case in which the elements of the 3D mesh $\mathcal{T}^{\Omega}_h$ do not conform with the surface $\Gamma$ nor with $\Lambda$. In this case, the 3D-1D-1D
formulation, namely Problem 2, is more suitable. 
%{\color{red} Add more details, we can refer also to cutFEM (Burman, Massing etc.) explaining the limitation of that approach (network case for example).}\\
Therefore we focus on the analysis of this discretization approach for Problem 2 solely.

\subsubsection{Problem 2} We consider for the solutions $u_h$ and ${\ud}_h$ the spaces $X_h = X_{h,0}^1(\Omega) \times X_{h^\prime,0}^1(\Lambda)$. With little abuse of notation, we assume that the characteristic mesh size of the 3D mesh $\mathcal{T}^{\Omega}_h$ and the one of the 1D mesh $\mathcal{T}^{\Lambda}_{h'}$ are different. Concerning the multiplier space, let $\mathcal{G}_h = \{K \in \mathcal{T}^{\Omega}_h: \, K\cap \Lambda \neq \emptyset\}$, be the set of the 3D elements that intersect $\Lambda$. Then we define $Q_h=\{{\ld}_h : {\ld}_h \in P^0(K) \, \forall K \in \mathcal{G}_h\}$. We notice that the multiplier functions are defined on the 3D elements. With little abuse of notation, we denote with $Q_h$ also the restriction to $\Lambda$ of the space of piecewise constant functions defined in 3D. As a result, we have $Q_h \subset L^2(\Lambda) \subset H^{-\frac12}(\Lambda)$.
With this choice of multipliers the problem is not inf-sup stable, therefore the idea is to add a stabilization term $s({\ld}_h, {\md}_h): \ Q_h \times Q_h \rightarrow \mathbb{R}$ to \eqref{eq:prob2_discrete} following the approach introduced in \cite{burman2014}. 
The objective of this section is to analyze the stabilized version of the 3D-1D-1D problem: find $[u_h, {\ud}_h] \in X_h$ and ${\ld}_h \in Q_h$ such that
\begin{multline}\label{eq:prob2_stabilized}
a([u_h, {\ud}_h], [v_h, {\vd}_h]) +
b([v_h, {\vd}_h], {\ld}_h)
+ b([u_h, {\ud}_h], {\md}_h)
- s({\ld}_h, {\md}_h) 
= c(v_h) + d({\md}_h)\\
  \quad \forall [v_h, {\vd}_h] \in X_h, \,
  \forall {\md}_h \in Q_h\,.
\end{multline}
The idea of the stabilization strategy proposed in \cite{burman2014}
is to identify a new multiplier space $Q_H$, which is never implemented in practice, such that inf-sup stability with $X_h$ holds true. Then, the stabilization operator is designed to control the distance between $Q_h$ and $Q_H$ trough the following inequality
\begin{equation*}
    \|{\md}_h - \pi_H {\md}_h\|_{Q_H} \leq C s_h({\md}_h, {\md}_h)\,,
\end{equation*}
being $\pi_H$ a suitable projection operator $Q_h \rightarrow Q_H$. Applying the results obtained in \cite{burman2014} we will show that the well posedness of problem \eqref{eq:prob2_stabilized} is governed by the following lemma.
\begin{lemma}[Lemma 2.3 of \cite{burman2014}]\label{lemma23burman}
\begin{enumerate}
    \item If the $b(\cdot,\cdot),\, X_h,Q_H \rightarrow \R$ is inf-sup stable.
    \item If the stabilization operator $s_h(\cdot,\cdot),\, Q_H,Q_H \rightarrow \R$ is such that
    \begin{equation*}
        \beta \|{\md}_h\|_{H^{-\frac12}(\Lambda)} \leq \sup\limits_{v_h \in X_h} \frac{b(v_h,{\md}_h}{\vertiii{v_h})} + s_h({\md}_h, {\md}_h), \quad \forall {\md}_h \in Q_h\,.
    \end{equation*}
    \item If for any $[v_h, {\vd}_h]$ there exists a function $\xi_h\in Q_h$ depending on $[v_h, {\vd}_h]$, namely $\xi_h=\xi_h([v_h, {\vd}_h])$, s.t.
\begin{gather}
\label{stab_coercivity}
a([v_h, {\vd}_h],[v_h, {\vd}_h] ) + b([v_h, {\vd}_h], \xi_h) \geq \alpha_\xi \vertiii{[v_h, {\vd}_h]}_{X_h}\,,
\\
\label{stab_stability}
(s(\xi_{h}, \xi_{h}))^{\frac 12} \leq c_s \vertiii{[v_h, {\vd}_h]}_{X_h}\,,
\end{gather}
being $\vertiii{[\cdot \, ,\, \cdot] }_{X_h}$ a suitable discrete norm. 
\end{enumerate}
Then, problem \eqref{eq:prob2_stabilized} admits a unique solution.
\end{lemma}
For the proof of this result we remand the reader to Lemma 2.3 of \cite{burman2014}. In the reminder of this section we show how to find a multiplier space $Q_H$ and a stabilization operator $s_h$ such that all the assumptions of lemma \ref{lemma23burman} are satisfied.

% The stabilization operator is based on a new multiplier space $Q_H$, for which the discrete inf-sup condition is fulfilled, and a projection operator $\pi_H: Q_h \rightarrow Q_H$ such that for any $[v, \vd] \in X $
% \begin{equation}\label{condition_pi_L}
% b([v, \vd], {\ld}_h - \pi_H {\ld}_h) \leq C \vertiii{[v,\vd]}\|{\ld}_h - \pi_H {\ld}_h\|_{Q_H},
% \end{equation}
% where for $X$ and $\vertiii{[\cdot, \cdot]}$ we use the definitions of section $3.2$ and $\|\cdot \|_{Q_H}$ denotes a suitable discrete norm on $Q_H$. Then, the following relaxed form of the inf-sup condition is satisfied,
% \begin{lemma}\cite[Lemma2.1]{burman2014}\label{lemma_burman2014}
% If the multiplier space $Q_H$ is inf-sup stable and the operator $\pi_H: Q_h \rightarrow Q_H$ satisfies \eqref{condition_pi_L}, then for any ${\ld}_h \in Q_h$ it holds,
% \begin{equation*}
% \|{\ld}_h\|_{H^{-\frac 12}(\Lambda)} \lesssim \sup_{\substack{v_h \in X_{h,0}^1(\Omega)\\ {\vd}_h \in X_{h^\prime,0}^1(\Lambda)}} \frac{b([v_h, {\vd}_h], {\ld}_h)}{\vertiii{[v_h, {\vd}_h]}} + \|{\ld}_h - \pi_H {\ld}_h\|_{Q_H}.
% \end{equation*}
% \end{lemma}
%  Based on this projection operator, we build the stabilization term $s({\ld}_h, {\md}_h)$ satisfying
%  \begin{equation}\label{condition_pi_L_bis}
%  \|{\ld}_h- \pi_H {\ld}_h\|_{Q_H} C \leq s({\ld}_h, {\ld}_h)
% \end{equation} and prove that for any $[u_h, {\ud}_h]$ there exists a function $\xi_h\in Q_h$ depending on $[u_h, {\ud}_h]$, namely $\xi_h=\xi_h([u_h, {\ud}_h])$, s.t.
% \begin{equation}\label{stab_coercivity}
% a([u_h, {\ud}_h],[u_h, {\ud}_h] ) + b([u_h, {\ud}_h], \xi_h) \geq \alpha_\xi \vertiii{[u_h, {\ud}_h]}_{X_{h,0}^1(\Omega)\times X_{h^\prime,0}^1(\Lambda) },
% \end{equation}
% \begin{equation}\label{stab_stability}
% (s(\xi_{h}, \xi_{h}))^{\frac 12} \leq c_s \vertiii{[u_h, {\ud}_h]}_{X_{h,0}^1(\Omega)\times X_{h^\prime,0}^1(\Lambda) },
% \end{equation}
% being $\vertiii{[\cdot \, ,\, \cdot] }_{X_{h,0}^1(\Omega)\times X_{h^\prime,0}^1(\Lambda) }$ a suitable discrete norm.

The first step consists of showing
that there exists a discrete space $Q_H$ that satisfies the first assumption of \ref{lemma23burman}. 
We recall that in the case of Problem 2, 
\begin{equation*}
b([u_h, {\vd}_h], {\md}_h) = \left(\mtrace v_h - {\vd}_h, {\md}_h\right)_{\Lambda,|\DD|}.
\end{equation*}
The construction of the inf-sup stable space $Q_H$ is based on macro elements of diameter $H$, where $H$ is sufficiently large. In particular, we assume that there exists positive constants $c_h$ and $c_H$ such that $c_h h\leq H \leq c_H^{-1}h$, being $h$ the mesh characteristic size of $\mathcal{T}_h^\Omega$. The space is constructed assembling the 3D elements of $\mathcal{G}_h$ into macro patches $ \patch $ such that $H \leq |\patch\cap \Lambda|\leq cH$, with $c\geq 1$. Let $M_j$ be the number of elements of the patch $\omega_j$, namely, $\patch=\cup _{i=0}^{M_j} K_i$, where $K_i \in \mathcal{G}_h$, $M_j$ is uniformly bounded in $j$ by some $M\in \mathbb{N}$ and $H=\min_{j}|\patch\cap \Lambda|$. We assume that the interiors of the patches $\patch$ are  disjoint. We define 
\begin{equation*}
Q_H=\left\{{\md }_H: \, {\md }_H\in P^0(\patch)\, \forall j \right\}.
\end{equation*}
As previously pointed out for $Q_h$, we denote with $Q_H$ also the restriction of the multiplier space to $\Lambda$, namely say $Q_H \subset L^2(\Lambda) \subset H^{-\frac12}(\Lambda)$.

@@

Moreover, we associate to each patch $\patch$ a shape-regular extended patch, still denoted by $\omega_j$ for notational simplicity, which is built adding to $\patch$ a sufficient number of elements of $\mathcal{T}_h^{\Omega}$ and we assume that the interiors of the new extended patches $\omega _j$ are still disjoint (see Figure \ref{fig:patch}). Here we are using the classical definition of shape-regularity, see for example \cite{MR2050138}, namely there exist a constant $C>0$ such that for any $\omega_j$, $\frac{\tilde{\rho}_j}{\bar{\rho}_j}\leq C$, being $\tilde{\rho}_j$ the diameter of $\omega_j$ and $\bar{\rho}_j$ the diameter of the largest ball that can be inscribed in $\omega_j$. The extended patches $\omega _j$ are built such that they fulfill the conditions meas$(\patch)=\mathcal{O}(H^3)$ and diam$(\Gamma_{\patch\cap \Lambda}\cap \omega_j)=\mathcal{O}(H)$, where $\Gamma_{\patch\cap \Lambda}$ is the portion of $\Gamma$ with centerline $\patch\cap \Lambda$. The latter assumption is required to ensure that the intersection of $\Gamma_{\patch\cap \Lambda}$ and $\omega_j$ is not too small and it will be needed later on to prove the inf-sup stability of the space $Q_H$ in Lemma \ref{lemma:Lh_infsup}. A representation of this construction in the simple case in which $\omega _j$ is composed just by one tetrahedron is shown in Figure \ref{fig:gamma_generated}.

% As shown in \cite[Section III]{burman2014}, we can always choose $\pi_H$ as the $L_2$ orthogonal projection operator from $\Lambda_h$ to $Q_H$ in order to satisfy \eqref{condition_pi_L} and then in practice replace it with any interpolation $\tilde{\pi}_L$ of $\Lambda_h$ in $Q_H$. In particular, for any $\lambda_h \in \Lambda_h$ we define,
% \begin{equation*}
% \tilde{\pi}_L {\ld}_{ _{|\patch}} = M_j^{-1} \sum_{\substack{i: \ K_i \in \mathcal{G}_h, \  K_i \cap \omega_j \neq \emptyset}} {\ld}_{|K_i} \qquad \text{for all $\omega_j$,} 
% \end{equation*}
% being $M_j$ the cardinality of the set $\{i: \ K_i \in \mathcal{G}_h, \  K_i \cap \omega_j \neq \emptyset\}$. These choices lead to the following stabilization 
% \begin{equation}\label{eq:stab}
% s({\ld}_h, {\md}_h)= \sum _{K\in \mathcal{G}_{h}} \int_{\partial K\setminus \partial \mathcal{G}_{h}} h \llbracket {\ld}_h \rrbracket \llbracket {\md}_h \rrbracket,
% \end{equation}
% being $\llbracket {\ld}_h \rrbracket$ the jump of ${\ld}_h$ across the internal faces of $\mathcal{G}_h$.

\begin{figure}\label{fig:gamma_generated}
\centering
\subfigure[$\Gamma_{\omega_j \cap \Lambda}$]
{
\input{./graphics/gamma_generated}
}
\qquad \qquad
\subfigure[ $\Gamma_{\omega_j \cap \Lambda} \cap \omega_j$]{
\input{./graphics/intersection}
}
\caption{$\Gamma_{\omega_j \cap \Lambda}$, the portion of $\Gamma$ generated by $\omega_j \cap \Lambda$ in (a) and the intersection between $\Gamma_{\omega_j \cap \Lambda}$ and $\omega_j$ in (b). Here for simplicity $\omega_j$ is represented as a single tetrahedron but actually it is a collection of tetrahedra as shown in Figure \ref{fig:patch}.}
\end{figure}

Thanks to the shape regularity of these extended patches, we have that the following discrete trace inequality holds true for any function $v\in H^1(\omega_j)$, 
\begin{equation}\label{discr_trace_ineq}
\|\trace v\|_{L^2(\Gamma\cap \omega_j)} \lesssim H^{-\frac 12} \|v\|_{L^2(\omega_j)}
\end{equation}
Moreover $\forall u_h \in X^1_{h,0}(\Omega)$ we have the following average inequality, which is a consequence of the definition of $\mtrace$ and Jensen inequality,
\begin{multline}\label{eq:avrg_ineq}
\sum _j \|\mtrace u_h\|^2_{L^2(\patch \cap \Lambda),|\DD| }
= \sum _j\int_{\patch \cap \Lambda} |\DD| \mtrace u_h^2 
= \int_{\Lambda} |\DD| \left( \frac{1}{|\DD|} \int_{\DD} \trace u_h \right)^2
\leq \int_{\Lambda} \int_{\DD} (\trace u_h)^2
\\
= \int_{\Gamma} (\trace u_h)^2
= \sum _j \int_{\patch \cap \Gamma} (\trace u_h)^2
= \sum _j \|\trace u_h\|^2_{L^2(\patch \cap \Gamma)}.
\end{multline}

We are now ready to prove that the space $Q_H$ is inf-sup stable. 
\begin{lemma}\label{lemma:Lh_infsup}
The space $Q_H$ is inf-sup stable, namely $\forall {\md}_H \in Q_H$, $\exists \beta >0$ s.t.
\begin{equation*}
\sup_{\substack{v_h \in X_{h,0}^1(\Omega),\\ {\vd}_h \in X_{h',0}^1(\Lambda)}} \frac{\left(\mtrace v_h - {\vd}_h, {\md} _H\right)_{\Lambda, |\DD|}}{\vertiii{[v_h, {\vd}_h]}} \geq \beta \|{\md}_H\|_{H^{-\frac 12}(\Lambda)}.
\end{equation*} 
\end{lemma}

\begin{proof}
As in the continuous case, we can choose ${\vd}_h=0$ and we prove that
\begin{equation*} 
\sup_{v_h \in X_{h,0}^1(\Omega)} \frac{\left(\mtrace v_h ,{\md}_H\right)_{\Lambda, |\DD|}}{\|v_h\|_{H^1(\Omega)}} \geq \beta \|{\md}_H\|_{H^{-\frac 12}(\Lambda)}.
\end{equation*} 
Proving the last inequality it is equivalent to find the Fortin operator $\pi_F: H^1_0(\Omega) \rightarrow X_{h,0}^1(\Omega)$, such that 
\begin{gather}
\left(\mtrace v - \mtrace \pi _F v  , {\md}_H\right)_{\Lambda, |\DD|}=0, \quad \forall v\in H^1_0(\Omega), \, {\md}_H \in Q_H\,,
\\
\label{eq:cont_Fortin}
\|\pi_F v\|_{H^1(\Omega)}\lesssim \|v\|_{H^1(\Omega)}\,.
\end{gather}

@@

\left(\mtrace v - \mtrace \pi _F v  , {\md}_H\right)_{\Lambda, |\DD|} = \sum _j \int_{\patch\cap \Lambda} |\DD |\left[ \mtrace v-\mtrace I_h v-\sum _i \alpha_i \mtrace \varphi _i \right]{\md}_H \\
(\text{supp} (\mtrace \varphi _i )\subset \omega _i\cap \Lambda \, \forall i)  =\sum _j \int_{\patch\cap \Lambda}|\DD| \left[ \mtrace v-\mtrace I_h v-\alpha_j \mtrace \varphi _j \right]{\md}_H\\
=\sum _j \int_{\patch\cap \Lambda} |\DD| (\mtrace v-\mtrace  I_h v) {\md}_H - \frac{\int_{\patch\cap \Lambda} |\DD| (\mtrace v-\mtrace I_h v)}{\int_{\patch\cap \Lambda}|\DD|\mtrace \varphi _j} \int_{\patch\cap \Lambda} |\DD|\mtrace \varphi _j{\md}_H\\ 
(\text{using ${\md}_H$ constant on $\patch\cap \Lambda$})=0.

@@

{\xi_h}_{|\patch\cap \Lambda}=\frac{\delta}{H} \pi_H(\mtrace u_h-{\ud}_h)_{|\patch \cap \Lambda}.

@@

Given $\pi_H,\ s_h(\cdot,\cdot), \ \xi_h$ defined above, the inequalities \eqref{stab_coercivity} and \eqref{stab_stability} are satisfied.

@@

Concerning the coercivity property \eqref{stab_coercivity}, we show that $\forall [u_h, {\ud}_h]$, there exists $\xi_h \in Q_h$ s.t.

@@

(u_h,u_h)_{H^1(\Omega)}+ ({\ud}_h, {\ud}_h)_{H^1(\Lambda), |\D|} +   (\mtrace u_h - {\ud}_h, \xi_h)_{\Lambda,|\DD|} \geq \alpha_{\xi}\vertiii{[u_h, {\ud}_h]}^2_{X_h}.

@@

and choosing $\delta=\frac{1}{2C}$ we obtain the desired inequality.\\
